Letter to the Editor

### 2022-10-27 editorial-communication/cover-letter-submission.Rmd
updates with preprint link
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@52a70b5c9cc16becb6a12e911a4d0a5793bdea18 🚀

We would like to submit our manuscript entitled “Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution” for consideration to be published in *Nature Ecology & Evolution*. 
Our study provides researchers with a critical review of twelve practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.

@@

Our manuscript is the most accessible and practical guide to using GitHub in ecology and evolution research to date.
We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
Also, we believe our manuscript complements a recently published manuscript in *Nature Ecology and Evolution*. In the manuscript, Gallagher et al. (2020) outline how the ongoing adoption of Open Science practices is transforming research in ecology and evolutionary biology. A key component of Open Science is the ability to collaboratively contribute to and share code and data--platforms like GitHub provide an free and accessible platform to do just that.

The enclosed manuscript is available as a preprint on the NAME OF SERVER AND CITATION, but is not published or in review elsewhere.
All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to *Nature Ecology & Evolution*.

@@

Rob Crystal-Ornelas PhD, on behalf of all co-authors

>>>>

We would like to submit our manuscript entitled “Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution” for consideration to be published in *Methods in Ecology and Evolution*. 
Our study provides researchers with a critical review of thirteen practical ways they can use GitHub – an online, cloud-based service for cooperative and documented code development – to make their research more collaborative, transparent, and reproducible.

@@

Our manuscript is the most accessible and practical guide to using GitHub in ecology and evolution research to date.
We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
Our manuscript is important for the *Methods in Ecology and Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our perspectives to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
Our manuscript also complements recently published literature outlining how the ongoing adoption of Open Science practices is transforming research in ecology and evolutionary biology.

The enclosed manuscript is available as a preprint on the MetaArXiv server (https://www.doi.org/10.31222/osf.io/x3p2q), with over 440 downloads and 2,400 views in four months. 
We declare that our study is not published or under consideration for publication elsewhere.

All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to Methods in Ecology and Evolution.

@@

Pedro Henrique Pereira Braga, on behalf of all co-authors
